Should I Airbnb My Property: Analytic Code Explanation

### 2018-05-22 scripts/3_data_prep.Rmd
bug fix: studyareasf obj

  # Study Area
  studyarea_sf <- suburb_sf %>% 
    slice(sa_ids) %>%
    st_union()
  plot(studyarea_sf)

@@

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        col_df, file=paste0(data_path, '/prepared/prepared_data.RData'))

>>>>

  # Study Area
  studyarea <- suburb_sf %>% 
    slice(sa_ids) %>%
    st_union()
  studyarea_sf <- st_sf(name='studyarea', geometry=studyarea)

  plot(studyarea_sf)

@@

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        col_df, clean_count, core_suburbs,
        file=paste0(data_path, '/prepared/prepared_data.RData'))

### 2018-05-22 scripts/4_data_analysis.Rmd
bug fix: studyareasf obj

  save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
       pot_glms, pot_ht_glms, lik_glms, lik_ht_glms, 
       file=file.path(data_path, 'analyzed', 'analyzed_data.RData'))

>>>>

  save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
       pot_glms, pot_ht_glms, lik_glms, lik_ht_glms, core_suburbs,
       file=file.path(data_path, 'analyzed', 'analyzed_data.RData'))
